Data Management \\ and LSST Special Programs

### 2022-02-21 DMTN-065.tex
fix LPG initials
fix hardbound camera quote

\author{M.~L.~Graham, M.~Juri\'{c}, K.-T.~Lim, E.~Bellm, G.~Dubois-Felsmann, L.~Guy, and the Data Management System Science Team}

@@

The minimum exposure time is 1 second (stretch goal: 0.1 seconds), and there is currently a hardware boundary that limits the readout rate to 1 every 15 seconds.
This would affect the image acquisition rate and increase the overheads of the proposed short-exposure micro-surveys.

>>>>

\author{M.~L.~Graham, M.~Juri\'{c}, K.-T.~Lim, E.~Bellm, G.~Dubois-Felsmann, L.~P.~Guy, and the Data Management System Science Team}

@@

The minimum exposure time is 1 second (stretch goal: 0.1 seconds), and there is a {\it potential} hardware boundary that limits the readout rate to 1 every 15 seconds.
This {\it might} affect the image acquisition rate and increase the overheads of the proposed short-exposure micro-surveys -- but current testing of the camera system indicates that imposing waits between short exposures will not be necessary.
